Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-03-07 ms.tex
I updated the plots and descriptions of the priors for looser priors so they're not driving the period too much.

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude flat amplitude model which essentially puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

Each of the light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

>>>>

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

Each of the light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 2.6 $< \tau < $3.6 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.7 $< \tau <$ 4.7 hr from \citet{2015ApJ...799..154M}, using wide 0.5 hr priors around the measured values.
These priors are used to ensure that the sinusoidal fits to not fit the airmass trends with time.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.
